Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-17 WSSSPE1_report/WSSSPE1_summary_report.tex
changes to conclusions, mostly

\subsection{Career Tracks for Scientific Software Developers} \note{lead: Daniel S. Katz} \label{sec:career-tracks}

Career track issues also came up repeatedly, starting in the the first keynote (\S\ref{sec:keynote1}), where Phil Bourne used the term ``the Google Bus'' to describe the issue of staff in his lab in San Diego who had chosen to leave science and work for Google (but since they didn't want to physically move, they take the Google bus to the Google office each day.)

@@

@@

@@

\note{say something about licensing - lessons, advice, etc.?}

\subsection{Top Issues}

\todo{what are the main issues discussed in each discussion section?, and what are the main common issues from the cross-cutting section - Dan to do that latter part}

\subsection{Recommendations or Lessons}

@@

\subsubsection{Workshop process}

>>>>

\subsection{Career Paths for Scientific Software Developers} \note{lead: Daniel S. Katz} \label{sec:career-tracks}

Career path issues also came up repeatedly, starting in the the first keynote (\S\ref{sec:keynote1}), where Phil Bourne used the term ``the Google Bus'' to describe the issue of staff in his lab in San Diego who had chosen to leave science and work for Google (but since they didn't want to physically move, they take the Google bus to the Google office each day.)

@@

\note{add a subsection about licensing - lessons, advice, etc.?}

@@

To conclude, we discuss the major concerns and issues that were raised in
the workshop, what we have learned, and what we plan to do going forward.

@@

\subsection{Concerns and issues}

\todo{what are the main issues discussed in each discussion section? - and, if you want, and recommendations on what should be done about them}

The issues that came up repeatedly in different parts of the workshop are, as described in
\S\ref{sec:cross-cutting}, the need for a definition of sustainability, and the need for
career paths for scientific software developers.

\subsection{Recommendations or lessons}

@@

\subsubsection*{Workshop process}
